Title Goes Here

### 2024-05-24 analysis/paper/paper.qmd
explore QS rankings

>>>>

```{r}
# explore QS rankings

qs_rankings <- 
  readxl::read_excel("analysis/data/raw_data/2024 QS WUR by Subject - Public Results (for qs.com)_48.xlsx", sheet = "Archaeology", skip = 12)

jobdata %>% 
  mutate(Institution = str_remove(name_of_hiring_university,
                                  " \\(.*\\)")) %>% 
  mutate(Institution = case_when(
    # modify the school name to match with the name in the QS list
    Institution == "Ohio State University-Main Campus" ~ "The Ohio State University",
    # ... 
    .default = as.character(Institution)
  )) %>% 
  select(Institution) %>% 
  left_join(qs_rankings) %>% 
  drop_na(`2024`) %>% 
  distinct(Institution, .keep_all = TRUE) %>% 
  View
